---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# golem.lint

<!-- badges: start -->
[![R-CMD-check](https://github.com/ThinkR-open/golem.lint/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/ThinkR-open/golem.lint/actions/workflows/R-CMD-check.yaml)

[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![Golemverse](https://img.shields.io/badge/Package%20of%20the%20Golemverse-8A2BE2)](https://golemverse.org/)
<!-- badges: end -->

**{golem.lint}** is a comprehensive linting package designed for R developers using the [Golem framework](https://github.com/ThinkR-open/golem) to build `Shiny` applications.

This package provides essential tools to help ensure your code adheres to best practices, enhancing the overall quality and maintainability of your applications.

## Features

- **Linting Tools**: Identify potential issues in your code, such as missing namespaces around IDs, ensuring your modules are well-structured.
- **Best Practices**: Promote adherence to coding standards and best practices specific to the Golem framework.
- **Improved Code Quality**: Enhance the reliability and maintainability of your `Shiny` applications through consistent linting.
- **Easy Integration**: Seamlessly integrate `golem.lint` into your existing Golem projects for a smooth development experience.

## Installation

You can install the development version of golem.lint from [GitHub](https://github.com/) with:

```{r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("ThinkR-open/golem.lint")
```


## Code of Conduct
  
Please note that the golem.lint project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html).

By contributing to this project, you agree to abide by its terms.
